### 2020-07-20 code/figure1.Rmd
Figure 1E data update - only umap3d coords objects change contents

mca_res <- MCA(
  X = gdc_path_mca[, pathway_list],
  ncp = optimal_dimensions, graph = FALSE
)

@@

rngtools::setRNG(r)
gdc.umap <- uwot::umap(mca_res$ind$coord, 
                       n_components = 3,
                       n_neighbors = round(sqrt(nrow(mca_res$ind$coord))), # 87
                       n_epochs = 1000,
                       n_threads = 1)
gdc_umap_coors <- as.data.frame(gdc.umap) %>%
  rename(plot_x = V1, plot_y = V2, plot_z = V3)

@@

####################
## Figure 1E data ##
####################
## To identify clusters using hdbscan, use umap in the third dimension
set.seed(3296)
gdc.umap.3d <- umap(gdc_path[,2:length(gdc_path)], n_components = 3)
gdc.umap.3d <- data.frame(x_3d = gdc.umap.3d$layout[,1], y_3d = gdc.umap.3d$layout[,2], z_3d = gdc.umap.3d$layout[,3]) ## coors of umap
rownames(gdc.umap.3d) <- gdc_path$sample ## insert sample_id in rownames
hdb_cluster_assignment <- hdbscan(gdc.umap.3d, minPts =  114) ## min group size for cluster is 114 (value before cluster number drops significantly)
umap_2d_3d_coors <- data.frame(x_2d = gdc_umap_coors$x_2d, y_2d = gdc_umap_coors$y_2d, x_3d = gdc.umap.3d$x_3d, y_3d = gdc.umap.3d$y_3d, z_3d = gdc.umap.3d$z_3d, clust = as.factor(hdb_cluster_assignment$cluster), member_prob = hdb_cluster_assignment$membership_prob, row.names = rownames(gdc.umap.3d)) ## clust 0 is unclassified cluster

>>>>

mca_res <- MCA(
  X = gdc_path_mca[, pathway_list],
  ncp = optimal_mca_dimensions, graph = FALSE
)

@@

rngtools::setRNG(r)
gdc.umap <- uwot::umap(mca_res$ind$coord, 
                       n_components = 3,
                       n_neighbors = round(sqrt(nrow(mca_res$ind$coord))), # 87
                       n_epochs = 1000,
                       n_threads = 1)
gdc_umap_coors <- as.data.frame(gdc.umap) %>%
  rename(plot_x = V1, plot_y = V2, plot_z = V3)
rownames(gdc_umap_coors) <- rownames(gdc_path_mca)

@@

####################
## Figure 1E data ##
####################
rngtools::setRNG(r)

cluster_umap <- uwot::umap(mca_res$ind$coord,
  min_dist = 1e-6,
  n_components = 3,
  n_neighbors = round(sqrt(nrow(mca_res$ind$coord))),
  n_epochs = 1000,
  n_threads = 1
)
colnames(cluster_umap) <- c("cluster_x", "cluster_y", "cluster_z")
hdb_cluster_assignment <- hdbscan(cluster_umap, minPts = optimal_minPts)
umap_3d_coors <- gdc_umap_coors %>%
  bind_cols(as.data.frame(cluster_umap)) %>%
  mutate(
    clust = as.factor(hdb_cluster_assignment$cluster),
    member_prob = hdb_cluster_assignment$membership_prob,
    row.names = rownames(gdc_umap_coors)
  )
## clust 0 is unclassified cluster
